A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-31 Paper/paper.tex
Put some tables in!

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage{caption}
\usepackage[disable]{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}

>>>>

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage{placeins}
\usepackage{caption}
\usepackage[disable]{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

\section{Framework Decision Matrices}

\FloatBarrier
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Async Support & Free & Separate Server & Assertion Styles & Test Interfaces & Reporters \\ \hline
Jasmine   & X             & X    &                 &                  &                 &           \\ \hline
Mocha     & X             & X    &                 & X*               & X               & X         \\ \hline
Qunit     & X             & X    &                 &                  &                 &           \\ \hline
Intern    & X             & X    & X               & X                & X               & X         \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Unit Testing Frameworks}
\end{table}
\FloatBarrier
\footnotesize

* Mocha requires a separate assertion, which leaves the options for assertion styles entirely up to the developer.

\FloatBarrier
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Free & GitHub & Other Repos & Multi-Language & Online & Beta \\ \hline
Jenkins   & X    & X*     & X*          & X*             & X*     &      \\ \hline
Travis    & X    & X      &             & X              & X      &      \\ \hline
Semaphore &      & X      &             & X              & X      &      \\ \hline
MagnumCI  & X    & X      & X           & X              & X      & X    \\ \hline
Drone.io  & X    & X      & X           & X              & X      &      \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier

* Jenkins has the ability to do all of the things listed with enough time devoted to setup.

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
